Automatic Matching of Bullet Lands

### 2015-12-29 imaging-paper.Rnw
eaning up ROC discussion

For smaller numbers of CMS, the percentage of false positives quickly increases. However, if we take other features of the image into account, we can increase the number of correct matches considerably: Figure~\ref{fig:densities} gives an overview of the densities of all of the features derived earlier, distinguishing between known matches (KM) and known non-matches (KNM). The densities of almost all of the features show strong differences between matches and non matches, e.g\ a high amount of cross-correlation between two signatures is indicative for a match --  in the Hamby study only known matches have a cross-correlation of 0.75 or higher. There are 97 land-to-land comparisons with a cross-correlation of above 0.75.

@@

Similarly, the Euclidean distance $D$ between two signatures is strongly correlated to known matches. Out of the 48 pairs of land-to-land signatures with a distance of less than .25, 47 correspond to known matches (the single known mismatch consists of a pair of signatures that both are very flat with peaks and valleys of less than 1.5$\mu m$). The average distance between known matches in the Hamby study is $\Sexpr{mean(bstats$D[bstats$match])}\mu m$ with a standard deviation of $\Sexpr{sd(bstats$D[bstats$match])}\mu m$; while known mismatches have an average  distance of  $\Sexpr{mean(bstats$D[!bstats$match])}\mu m$ with a standard deviation of $\Sexpr{sd(bstats$D[!bstats$match])}\mu m$.
All of the features in Figure~\ref{fig:densities} show large, if not significant, differences between matches and non-matches. Table~\ref{tab:importance} shows an overview in the averages and corresponding standard deviations of  a set of feature variables derived from the 3d topological surface measurements. There are quite large differences in these averages, indicating that we can successfully employ machine learning methods to distinguish matches from non-matches.

>>>>

For smaller numbers of CMS, the percentage of false positives quickly increases. However, if we take other features of the image into account, we can increase the number of correct matches considerably: Figure~\ref{fig:densities} gives an overview of the densities of all of the features derived earlier, distinguishing between known matches (KM) and known non-matches (KNM). The densities of almost all of the features show strong differences between matches and non matches. For example, a high amount of cross-correlation between two signatures is indicative for a match --  in the Hamby study only known matches have a cross-correlation of 0.75 or higher. There are 97 land-to-land comparisons with a cross-correlation that high.

@@

Similarly, the Euclidean distance $D$ between two signatures is strongly correlated to known matches. Out of the 48 pairs of land-to-land signatures with a distance of less than .25, 47 correspond to known matches (the single known mismatch consists of a pair of signatures that both are very flat with peaks and valleys of less than 1.5$\mu m$). %The average distance between known matches in the Hamby study is $\Sexpr{mean(bstats$D[bstats$match])}\mu m$ with a standard deviation of $\Sexpr{sd(bstats$D[bstats$match])}\mu m$; while known mismatches have an average  distance of  $\Sexpr{mean(bstats$D[!bstats$match])}\mu m$ with a standard deviation of $\Sexpr{sd(bstats$D[!bstats$match])}\mu m$.
All of the features in Figure~\ref{fig:densities} show large, if not significant, differences between matches and non-matches. The predictive power of each one of these features is shown in form of ROC curves in Figure~\ref{fig:rocs}. The features are ordered according to the area under the curve (AUC). The feature with the highest individual predictive power is $S$, the sum of two signatures' heights of joint peaks and valleys. The maximal number of CMS is only in the seventh position here. The overall high AUC values indicate, that we can successfully employ machine learning methods to distinguish matches from non-matches.
%Table~\ref{tab:importance} shows an overview in the averages and corresponding standard deviations of the set of feature variables derived in section~\ref{sec:algorithm} from the 3d topological surface measurements. There are quite large differences in these averages, indicating
